\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-11-18 paper.qmd
Regenerate MSE plots
Changed the script to view the true model along with the data

```{r}
#| label: two-curvy-training
training_data_two_curvy <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_data.rds")
```

@@

true_model_df <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_true_model.rds")
wireframe_true_model <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_true_model_connections.rds")

@@

<!--UMAP applied for Two curvy data-->
```{r}
#| label: umap-two-curvy
umap_two_curvy <- read_rds(file = "data/two_c_shaped_clust/two_c_shaped_clust_umap_n-neigbors_15_min-dist_0.1.rds")

@@

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 15

@@

error_two_c_shaped_clust_umap <- read_rds("data/two_c_shaped_clust/error_two_c_shaped_clust_umap.rds")

## Find the minimum MSE when have duplicate a1
error_two_c_shaped_clust_umap <- error_two_c_shaped_clust_umap |>
  group_by(a1) |>
  filter(bin1 == min(bin1)) |>
  ungroup() |>
  mutate(prop_dens = 1/(b*side_length^2))

base_line_prop_dens <- error_two_c_shaped_clust_umap |>
  filter(a1 == min(a1)) |>
  pull(prop_dens)

error_two_c_shaped_clust_umap <- error_two_c_shaped_clust_umap |>
  mutate(prop_comp = prop_dens/base_line_prop_dens)

mse_two_curvy_b <- ggplot(error_two_c_shaped_clust_umap, 
                     aes(x = a1, 
                         y = MSE)) +
  geom_vline(xintercept = 0.09,
             linetype="solid",
           color = "#d95f02", linewidth=1) +
  geom_vline(xintercept = 0.05,
             color = "#1b9e77", linetype=2,
             linewidth=1) +
  geom_vline(xintercept = 0.13, linetype=2,
             color = "#1f78b4", linewidth=1) +
  geom_line(linewidth = 0.5) + 
  geom_point(size = 1) +
  scale_x_continuous(breaks = sort(unique(round(error_two_c_shaped_clust_umap$a1, 2)))[c(1, 4, 8, 10, 11, 12, 13, 14)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = "MSE") +
  ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

prop_dens_a1 <- ggplot(error_two_c_shaped_clust_umap,
                     aes(x = a1,
                         y = prop_comp)) +
  geom_vline(xintercept = 0.09,
             linetype="solid",
           color = "#d95f02", linewidth=1) +
  geom_vline(xintercept = 0.05,
             color = "#1b9e77", linetype=2,
             linewidth=1) +
  geom_vline(xintercept = 0.13, linetype=2,
             color = "#1f78b4", linewidth=1) +
  geom_line(linewidth = 0.5) +
  geom_point(size = 1) +
  # scale_y_continuous(breaks = sort(unique(error_two_curvy$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_two_c_shaped_clust_umap$a1, 2)))[c(1, 4, 8, 10, 11, 12, 13, 14)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = paste("Relative proportion density")) +
  ggtitle("(d)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

error_two_c_shaped_clust_umap <- error_two_c_shaped_clust_umap |>
  mutate(prop_bins = b_non_empty/b)

a1_m_two_curvy <- ggplot(error_two_c_shaped_clust_umap,
                     aes(x = a1,
                         y = prop_bins)) +
  geom_vline(xintercept = 0.09,
             linetype="solid",
           color = "#d95f02", linewidth=1) +
  geom_vline(xintercept = 0.05,
             color = "#1b9e77", linetype=2,
             linewidth=1) +
  geom_vline(xintercept = 0.13, linetype=2,
             color = "#1f78b4", linewidth=1) +
  geom_line(linewidth = 0.5) +
  geom_point(size = 1) +
  # scale_y_continuous(breaks = sort(unique(error_two_curvy$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_two_c_shaped_clust_umap$a1, 2)))[c(1, 4, 8, 10, 11, 12, 13, 14)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = expression(paste("proportion of non-empty bins ", bgroup("(", frac(m, b), ")")))) +
  ggtitle("(b)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

predict_umap_two_curvy <- read_rds(file = "data/two_c_shaped_clust/two_c_shaped_clust_umap_predict_true.rds")

@@

error_rm_two_curvy <- read_rds("data/two_c_shaped_clust/error_rm_lwd_diff_bin.rds") |>
  mutate(bin1  = as.factor(bin1))

@@

```{r}
#| label: read-two-curvy-clust-nldr
# Read a variety of different NLDR representations of two_c_shaped_clust
# and plot them on same aspect ratio
tsne_two_c_shaped_clust <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_tsne_perplexity_30.rds")

nldr_two_c_shaped_clust1 <- tsne_two_c_shaped_clust |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("a", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

umap_two_c_shaped_clust <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_umap_n-neigbors_15_min-dist_0.1.rds")

nldr_two_c_shaped_clust2 <- umap_two_c_shaped_clust |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour='#636363') +
  interior_annotation("b", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

phate_two_c_shaped_clust <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_phate_knn_5.rds")

nldr_two_c_shaped_clust3 <- phate_two_c_shaped_clust |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  interior_annotation("c") +
  theme(aspect.ratio = 1)

trimap_two_c_shaped_clust <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_trimap_n-inliers_12_n-outliers_4_n-random_3.rds")

nldr_two_c_shaped_clust4 <- trimap_two_c_shaped_clust |>
  ggplot(aes(x = TriMAP1,
             y = TriMAP2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  interior_annotation("d") +
  theme(aspect.ratio = 1)

pacmap_two_c_shaped_clust <- read_rds("data/two_c_shaped_clust/two_c_shaped_clust_pacmap_n-neighbors_10_init_random_MN-ratio_0.5_FP-ratio_2.rds")

nldr_two_c_shaped_clust5 <- pacmap_two_c_shaped_clust |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("e") +
  theme(aspect.ratio = 1)
```

```{r}
#| label: combine-data-two_c_shaped_clust

error_two_c_shaped_clust_umap <- read_rds("data/two_c_shaped_clust/error_two_c_shaped_clust_umap.rds")
error_two_c_shaped_clust_tsne <- read_rds("data/two_c_shaped_clust/error_two_c_shaped_clust_tsne.rds")
error_two_c_shaped_clust_phate <- read_rds("data/two_c_shaped_clust/error_two_c_shaped_clust_phate.rds")
error_two_c_shaped_clust_trimap <- read_rds("data/two_c_shaped_clust/error_two_c_shaped_clust_trimap.rds")
error_two_c_shaped_clust_pacmap <- read_rds("data/two_c_shaped_clust/error_two_c_shaped_clust_pacmap.rds")

error_two_c_shaped_clust <- bind_rows(error_two_c_shaped_clust_umap, 
                         error_two_c_shaped_clust_tsne,
                         error_two_c_shaped_clust_phate,
                         error_two_c_shaped_clust_trimap,
                         error_two_c_shaped_clust_pacmap)

error_two_c_shaped_clust <- error_two_c_shaped_clust |>
  mutate(a1 = round(a1, 2)) |>
  filter(bin1 >= 5) |>
  group_by(method, a1) |>
  filter(MSE == min(MSE)) |>
  ungroup()
```

```{r}
#| label: error-comp-two_c_shaped_clust

error_plot_two_c_shaped_clust <- ggplot(error_two_c_shaped_clust, 
                           aes(x = a1, 
                               y = MSE, 
                               colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_two_c_shaped_clust$a1))[seq(1, length(unique(error_two_c_shaped_clust$a1)), by = 5)]) +
  scale_color_manual(values=c('#e41a1c','#ff7f00','#4daf4a', "#a65628",'#636363')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

```{r}
#| fig-cap: "Assessing which of the 5 NLDR layouts on the two C-shaped clusters data is the better representation using MSE for varying binwidth ($a_1$). Colour used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-e). Layout d is universally poor. Layouts a that show two close clusters are universally suboptimal. Layout a is the best choice."
#| label: fig-two_c_shaped_clust-mse
#| fig-pos: H
#| out-height: 60%

free(error_plot_two_c_shaped_clust) + wrap_plots(nldr_two_c_shaped_clust1, nldr_two_c_shaped_clust2, nldr_two_c_shaped_clust3, 
                                    nldr_two_c_shaped_clust4, nldr_two_c_shaped_clust5, ncol = 2)
```

@@

two_curvy_tsne_scaled_obj <- gen_scaled_data(
  data = tsne_two_c_shaped_clust)

@@

tsne_two_c_shaped_clust_plt <- tsne_two_curvy_scaled |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("b1", sc_ltr_pos) +
  theme(aspect.ratio = 1)

@@

two_curvy_pacmap_scaled_obj <- gen_scaled_data(
  data = pacmap_two_c_shaped_clust)

@@

pacmap_two_c_shaped_clust_plt <- pacmap_two_curvy_scaled |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("c1", sc_ltr_pos) +
  theme(aspect.ratio = 1)

@@

nldr_two_curvy_original2 + tsne_two_c_shaped_clust_plt +
  pacmap_two_c_shaped_clust_plt +
  trimesh_two_curvy_removed1_with_data + trimesh_two_curvy_removed1_tsne_with_data +
trimesh_two_curvy_removed1_pacmap_with_data +
  two_curvy_proj_umap_model2 +
  two_curvy_proj_tsne_model +
  two_curvy_proj_pacmap_model +
  two_curvy_proj_umap_all_model +
  two_curvy_proj_tsne_all_model +
  two_curvy_proj_pacmap_all_model +
  plot_layout(ncol = 3) +
  plot_annotation(tag_levels = list(c("(a)", "(b)", "(c)")))
```

>>>>

```{r}
#| label: two-curvy-training
training_data_two_curvy <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_data.rds")
```

@@

true_model_df <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_true_model.rds")
wireframe_true_model <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_true_model_connections.rds")

@@

<!--UMAP applied for Two curvy data-->
```{r}
#| label: umap-two-curvy
umap_two_curvy <- read_rds(file = "data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_umap_n-neigbors_15_min-dist_0.1.rds")

@@

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 12

@@

error_two_non_linear_diff_shaped_close_clusters_umap <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_umap.rds")

## Find the minimum MSE when have duplicate a1
error_two_non_linear_diff_shaped_close_clusters_umap <- error_two_non_linear_diff_shaped_close_clusters_umap |>
  group_by(a1) |>
  filter(bin1 == min(bin1)) |>
  ungroup() |>
  mutate(prop_dens = 1/(b*side_length^2))

base_line_prop_dens <- error_two_non_linear_diff_shaped_close_clusters_umap |>
  filter(a1 == min(a1)) |>
  pull(prop_dens)

error_two_non_linear_diff_shaped_close_clusters_umap <- error_two_non_linear_diff_shaped_close_clusters_umap |>
  mutate(prop_comp = prop_dens/base_line_prop_dens)

mse_two_curvy_b <- ggplot(error_two_non_linear_diff_shaped_close_clusters_umap, 
                     aes(x = a1, 
                         y = MSE)) +
  geom_vline(xintercept = 0.09,
             linetype="solid",
           color = "#d95f02", linewidth=1) +
  geom_vline(xintercept = 0.05,
             color = "#1b9e77", linetype=2,
             linewidth=1) +
  geom_vline(xintercept = 0.13, linetype=2,
             color = "#1f78b4", linewidth=1) +
  geom_line(linewidth = 0.5) + 
  geom_point(size = 1) +
  scale_x_continuous(breaks = sort(unique(round(error_two_non_linear_diff_shaped_close_clusters_umap$a1, 2)))[c(1, 4, 8, 10, 11, 12, 13, 14)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = "MSE") +
  ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

prop_dens_a1 <- ggplot(error_two_non_linear_diff_shaped_close_clusters_umap,
                     aes(x = a1,
                         y = prop_comp)) +
  geom_vline(xintercept = 0.09,
             linetype="solid",
           color = "#d95f02", linewidth=1) +
  geom_vline(xintercept = 0.05,
             color = "#1b9e77", linetype=2,
             linewidth=1) +
  geom_vline(xintercept = 0.13, linetype=2,
             color = "#1f78b4", linewidth=1) +
  geom_line(linewidth = 0.5) +
  geom_point(size = 1) +
  # scale_y_continuous(breaks = sort(unique(error_two_curvy$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_two_non_linear_diff_shaped_close_clusters_umap$a1, 2)))[c(1, 4, 8, 10, 11, 12, 13, 14)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = paste("Relative proportion density")) +
  ggtitle("(d)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

error_two_non_linear_diff_shaped_close_clusters_umap <- error_two_non_linear_diff_shaped_close_clusters_umap |>
  mutate(prop_bins = b_non_empty/b)

a1_m_two_curvy <- ggplot(error_two_non_linear_diff_shaped_close_clusters_umap,
                     aes(x = a1,
                         y = prop_bins)) +
  geom_vline(xintercept = 0.09,
             linetype="solid",
           color = "#d95f02", linewidth=1) +
  geom_vline(xintercept = 0.05,
             color = "#1b9e77", linetype=2,
             linewidth=1) +
  geom_vline(xintercept = 0.13, linetype=2,
             color = "#1f78b4", linewidth=1) +
  geom_line(linewidth = 0.5) +
  geom_point(size = 1) +
  # scale_y_continuous(breaks = sort(unique(error_two_curvy$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_two_non_linear_diff_shaped_close_clusters_umap$a1, 2)))[c(1, 4, 8, 10, 11, 12, 13, 14)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = expression(paste("proportion of non-empty bins ", bgroup("(", frac(m, b), ")")))) +
  ggtitle("(b)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

predict_umap_two_curvy <- read_rds(file = "data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_umap_predict_true.rds")

@@

error_rm_two_curvy <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_rm_lwd_diff_bin.rds") |>
  mutate(bin1  = as.factor(bin1))

@@

```{r}
#| label: read-two-curvy-clust-nldr
# Read a variety of different NLDR representations of two_non_linear_diff_shaped_close_clusters
# and plot them on same aspect ratio
tsne_two_non_linear_diff_shaped_close_clusters <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_tsne_perplexity_30.rds")

nldr_two_non_linear_diff_shaped_close_clusters1 <- tsne_two_non_linear_diff_shaped_close_clusters |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("a", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

umap_two_non_linear_diff_shaped_close_clusters <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_umap_n-neigbors_15_min-dist_0.1.rds")

nldr_two_non_linear_diff_shaped_close_clusters2 <- umap_two_non_linear_diff_shaped_close_clusters |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour='#636363') +
  interior_annotation("b", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

phate_two_non_linear_diff_shaped_close_clusters <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_phate_knn_5.rds")

nldr_two_non_linear_diff_shaped_close_clusters3 <- phate_two_non_linear_diff_shaped_close_clusters |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  interior_annotation("c") +
  theme(aspect.ratio = 1)

trimap_two_non_linear_diff_shaped_close_clusters <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_trimap_n-inliers_12_n-outliers_4_n-random_3.rds")

nldr_two_non_linear_diff_shaped_close_clusters4 <- trimap_two_non_linear_diff_shaped_close_clusters |>
  ggplot(aes(x = TriMAP1,
             y = TriMAP2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  interior_annotation("d") +
  theme(aspect.ratio = 1)

pacmap_two_non_linear_diff_shaped_close_clusters <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_pacmap_n-neighbors_10_init_random_MN-ratio_0.5_FP-ratio_2.rds")

nldr_two_non_linear_diff_shaped_close_clusters5 <- pacmap_two_non_linear_diff_shaped_close_clusters |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("e") +
  theme(aspect.ratio = 1)
```

```{r}
#| label: combine-data-two_non_linear_diff_shaped_close_clusters

error_two_non_linear_diff_shaped_close_clusters_umap <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_umap.rds")
error_two_non_linear_diff_shaped_close_clusters_tsne <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_tsne.rds")
error_two_non_linear_diff_shaped_close_clusters_phate <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_phate.rds")
error_two_non_linear_diff_shaped_close_clusters_trimap <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_trimap.rds")
error_two_non_linear_diff_shaped_close_clusters_pacmap <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_pacmap.rds")

error_two_non_linear_diff_shaped_close_clusters <- bind_rows(error_two_non_linear_diff_shaped_close_clusters_umap, 
                         error_two_non_linear_diff_shaped_close_clusters_tsne,
                         error_two_non_linear_diff_shaped_close_clusters_phate,
                         error_two_non_linear_diff_shaped_close_clusters_trimap,
                         error_two_non_linear_diff_shaped_close_clusters_pacmap)

error_two_non_linear_diff_shaped_close_clusters <- error_two_non_linear_diff_shaped_close_clusters |>
  mutate(a1 = round(a1, 2)) |>
  filter(bin1 >= 5) |>
  group_by(method, a1) |>
  filter(MSE == min(MSE)) |>
  ungroup()
```

```{r}
#| label: error-comp-two_non_linear_diff_shaped_close_clusters

error_plot_two_non_linear_diff_shaped_close_clusters <- ggplot(error_two_non_linear_diff_shaped_close_clusters, 
                           aes(x = a1, 
                               y = MSE, 
                               colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_two_non_linear_diff_shaped_close_clusters$a1))[seq(1, length(unique(error_two_non_linear_diff_shaped_close_clusters$a1)), by = 5)]) +
  scale_color_manual(values=c('#e41a1c','#ff7f00','#4daf4a', "#a65628",'#636363')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

```{r}
#| fig-cap: "Assessing which of the 5 NLDR layouts on the two C-shaped clusters data is the better representation using MSE for varying binwidth ($a_1$). Colour used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-e). Layout d is universally poor. Layouts a that show two close clusters are universally suboptimal. Layout a is the best choice."
#| label: fig-two_non_linear_diff_shaped_close_clusters-mse
#| fig-pos: H
#| out-height: 60%

free(error_plot_two_non_linear_diff_shaped_close_clusters) + wrap_plots(nldr_two_non_linear_diff_shaped_close_clusters1, nldr_two_non_linear_diff_shaped_close_clusters2, nldr_two_non_linear_diff_shaped_close_clusters3, 
                                    nldr_two_non_linear_diff_shaped_close_clusters4, nldr_two_non_linear_diff_shaped_close_clusters5, ncol = 2)
```

@@

two_curvy_tsne_scaled_obj <- gen_scaled_data(
  data = tsne_two_non_linear_diff_shaped_close_clusters)

@@

tsne_two_non_linear_diff_shaped_close_clusters_plt <- tsne_two_curvy_scaled |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("b1", sc_ltr_pos) +
  theme(aspect.ratio = 1)

@@

two_curvy_pacmap_scaled_obj <- gen_scaled_data(
  data = pacmap_two_non_linear_diff_shaped_close_clusters)

@@

pacmap_two_non_linear_diff_shaped_close_clusters_plt <- pacmap_two_curvy_scaled |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("c1", sc_ltr_pos) +
  theme(aspect.ratio = 1)

@@

nldr_two_curvy_original2 + tsne_two_non_linear_diff_shaped_close_clusters_plt +
  pacmap_two_non_linear_diff_shaped_close_clusters_plt +
  trimesh_two_curvy_removed1_with_data + trimesh_two_curvy_removed1_tsne_with_data +
trimesh_two_curvy_removed1_pacmap_with_data +
  two_curvy_proj_umap_model2 +
  two_curvy_proj_tsne_model +
  two_curvy_proj_pacmap_model +
  two_curvy_proj_umap_all_model +
  two_curvy_proj_tsne_all_model +
  two_curvy_proj_pacmap_all_model +
  plot_layout(ncol = 3) +
  plot_annotation(tag_levels = list(c("(a)", "(b)", "(c)")))
```

### 2024-11-18 paper.tex
Changed the script to view the true model along with the data

\includegraphics[width=1\textwidth,height=0.6\textheight]{paper_files/figure-pdf/fig-two_c_shaped_clust-mse-1.pdf}

@@

\caption{\label{fig-two_c_shaped_clust-mse}Assessing which of the 5 NLDR
layouts on the two C-shaped clusters data is the better representation
using MSE for varying binwidth (\(a_1\)). Colour used for the lines and
points in the left plot and in the scatterplots represents NLDR layout
(a-e). Layout d is universally poor. Layouts a that show two close
clusters are universally suboptimal. Layout a is the best choice.}

>>>>

\includegraphics[width=1\textwidth,height=0.6\textheight]{paper_files/figure-pdf/fig-two_non_linear_diff_shaped_close_clusters-mse-1.pdf}

@@

\caption{\label{fig-two_non_linear_diff_shaped_close_clusters-mse}Assessing
which of the 5 NLDR layouts on the two C-shaped clusters data is the
better representation using MSE for varying binwidth (\(a_1\)). Colour
used for the lines and points in the left plot and in the scatterplots
represents NLDR layout (a-e). Layout d is universally poor. Layouts a
that show two close clusters are universally suboptimal. Layout a is the
best choice.}
